HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-03-31 LaTeX/ms.tex
Added appendix with SPIRE fluxes

\caption{ Model fits for each target in the {\it Herschel}-ALMA sample, 3
panels per target.  {\it Left}: ALMA 870$\mu$m imaging (red contours, starting
at $\pm 3\sigma$ and increasing by factors of 2) overlaid on best available
optical or near-IR imaging (grayscale, with telescope and filter printed in
upper right corner).  The location and morphology of all sources used in the
model are represented by magenta ellipses.  If a lens is present, its location
is given by a black circle and its critical curve is traced by an orange line.
The FWHM size of the ALMA synthesized beam is shown in the lower left corner of
each panel.  {\it Middle}: Same as {\it left}, but showing best-fit model in
grayscale.  {\it Right}: Same as {\it left}, but showing resdiual image
obtained from subtracting best-fit model from the data.  \label{fig:uvmodels}}
\addtocounter{figure}{-1}

@@

For comparison, we also show the cumulative distribution of $S_{870}$ for the
ALESS sample.  ALESS is the only existing sample of DSFGs with interferometric
follow-up of a sensitivity and angular resolution that is comparable to our
ALMA data, so it is the best sample with which to compare our results.  There
is greater overlap in $S_{870}$ between our sample and ALESS than there is in
$S_{500}$ (recall Figure~\ref{fig:sample}).  This is evidence that the DSFGs in
our sample have higher $S_{500}/S_{870}$ ratios than the DSFGs in ALESS.  This
difference is likely due to differences in dust temperature and/or redshift
distributions of the two samples and probably arises from selection effects.

@@

A related but distinct test of the intrinsic luminosity functions for DSFGs
comes from the probability of a given source experiencing a magnification above
some threshold value, $\mu_{\rm min}$.  Unlike the case with the average
magnification factor measurements, our ALMA and SMA data should provide a
reliable estimate of this quantity.  The results of this are shown in the right
panel of Figure~\ref{fig:lensstats}.  For clarity of presentation, we show one
choice of $\mu_{\rm min}$: $\mu_{\rm min} = 2.0$.  The shape of the curves
varies with  $\mu_{\rm min}$, but the overall results are qualitatively the
same.  The models we consider are the same as those used in the left panel of
Figure~\ref{fig:lensstats}.  Instead of computing a running average of the
data, we show a logistic regression fit to the data \citep[obtained with the
{\sc Scikit-learn package;][]{scikit-learn}.

@@

%\appendix

>>>>

\caption{ Model fits for each target in the {\it Herschel}-ALMA sample, 3
panels per target.  {\it Left}: ALMA 870$\mu$m imaging (red contours, starting
at $\pm 3\sigma$ and increasing by factors of 2) overlaid on best available
optical or near-IR imaging (grayscale, with telescope and filter printed in
upper right corner).  The location and morphology of all sources used in the
model are represented by magenta ellipses.  If a lens is present, its location
is given by a black circle and its critical curve is traced by an orange line.
The FWHM size of the ALMA synthesized beam is shown in the lower left corner of
each panel.  {\it Middle}: Same as {\it left}, but showing best-fit model in
grayscale.  {\it Right}: Same as {\it left}, but showing residual image
obtained from subtracting best-fit model from the data.  \label{fig:uvmodels}}
\addtocounter{figure}{-1}

@@

For comparison, we also show the cumulative distribution of $S_{870}$ for the
ALESS sample.  ALESS is the only existing sample of DSFGs with interferometric
follow-up of a sensitivity and angular resolution that is comparable to our
ALMA data, so it is the best sample with which to compare our results.  The
significant overlap in $S_{870}$ between our sample and ALESS is evidence that
the DSFGs in our sample have higher $S_{500}/S_{870}$ ratios than the DSFGs in
ALESS (recall Figure~\ref{fig:sample}, which shows that ALESS sources have much
lower $S_{500}$ than our targets).  This difference is likely due to
differences in dust temperature and/or redshift distributions of the two
samples and probably arises from selection effects.

@@

A related but distinct test of the intrinsic luminosity functions for DSFGs
comes from the probability of a given source experiencing a magnification above
some threshold value, $\mu_{\rm min}$.  Unlike the case with the average
magnification factor measurements, our ALMA and SMA data should provide a
reliable estimate of this quantity.  The results of this are shown in the right
panel of Figure~\ref{fig:lensstats}.  For clarity of presentation, we show one
choice of $\mu_{\rm min}$: $\mu_{\rm min} = 2.0$.  The shape of the curves
varies with  $\mu_{\rm min}$, but the overall results are qualitatively the
same.  The models we consider are the same as those used in the left panel of
Figure~\ref{fig:lensstats}.  Instead of computing a running average of the
data, we show a logistic regression fit to the data \citep[obtained with the
{\sc Scikit-learn} package;][]{scikitlearn}.

@@

\appendix

\section{{\it Herschel}/SPIRE Photometry}

We present in Table~\ref{tab:photometry} SPIRE photometry ($S_{250}$,
$S_{350}$, and $S_{500}$) for each {\it Herschel} source in our sample using as
priors the ALMA and {\it Spitzer} 24$\,\mu$m counterpart positions.  Many of
the {\it Herschel} sources in our sample have multiple 24$\,\mu$m counterparts
close enough to the ALMA counterparts that they can make a significant
contribution to the SPIRE flux at the position of the ALMA counterparts.  For
this reason, it is critical to include the 24$\,\mu$m data when estimating {\it
Herschel}/SPIRE photometry.  In cases where the {\it Spitzer} 24$\,\mu$m and
ALMA counterparts spatially overlap (defined here as having a separation
smaller than $2\farcs5$), we exclude the {\it Spitzer} counterpart from the
calculations.

Note that in the case of HELAISS02, we exclude a 24$\,\mu$m source associated
with the lensing galaxy, despite being more than $2\farcs5$ away from the
nearest ALMA counterpart.  This is because the ALMA counterparts are arranged
so that they surround the 24$\mu$m source completely.  The extended emission
seen in the SPIRE maps is therefore most likely attributable to the ALMA
counterparts rather than the 24$\,\mu$m source.

One of the key results from this analysis is that the use of StarFinder to
deconvolve the SPIRE beam will lead to the removal of a portion of the targets
with extended emission from a flux-limited sample.  This is by design, as the
goal outlined in \citet{Wardlow:2013lr} was to develop the purest sample of
lens candidates as possible from HerMES data.  Blends were considered by these
authors to be unlikely to be lensed.  This method is effective for lenses where
the Einstein radius is smaller than $\approx 2\arcsec$.  However, it selects
against deeper potential wells, such as those of groups or clusters
\citep[e.g., HLock01][]{Gavazzi:2011lr}, that produce images separated by
scales that comprise a significant fraction of the SPIRE PSF.

It is worth emphasizing that blends likely constitute an interesting path of
study for future work, as they potentially represent proto-groups or
proto-clusters during a particular active stage of their evolution.  They are
also prime examples of systems of sources that are poorly reproduced in
simulations, as evidenced by the investigations in
Section~\ref{sec:spatialdist} in this paper.  Table~\ref{tab:photometry} shows
that one possible means of selecting candidate blends is by comparing the
SUSSEXtractor and StarFinder flux densities, particularly at 500$\,\mu$m.  A
large difference between these two measurements likely indicates multiple
components separated by scales that are a significant fraction of the SPIRE
beam (e.g., HELAISS02, HXMM20, and HCOSMOS02).

\clearpage
\input{table_photometry}
